---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# ggtetris

[![Travis build status](https://travis-ci.org/EmilHvitfeldt/ggtetris.svg?branch=master)](https://travis-ci.org/EmilHvitfeldt/ggtetris)

The goal of ggtetris is to add a fun alternative to `geom_bar` that stack squared together to represent groups. This happens to have a resemblance to a tetris board hence name.  

It used ggplot2 and returns a ggplot2 object.  

The main star of the package is `ggtetris()` that produces a finished chart from a variety of inputs. 
In addition the package also provides the `ggtetris_tidy()` function that transform the inputs of `ggtetris()` into a tidy format. `tetris_color()` provides a range of color schemes and the `scale_*_tetris()` family will allow you to use those color palettes directly to ggplot2.

## Installation

You can install ggtetris from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/ggtetris")
```

## Examples

```{r}
library(ggtetris)
```

### Unnamed vectors

```{r example}
counts <- rep(5, 10)
ggtetris(counts)
```

```{r}
ggtetris(counts, colunms = 6)
```

```{r}
raw_data <- rpois(100, lambda = 1)
counts <- table(raw_data)
ggtetris(counts, colors = tetris_color(palette = "Microsoft"), line_color = "black")
```


### Named vectors

```{r}
ggtetris(c('AA' = 30, 'BB' = 23, 'CC' = 10))
```

```{r}
ggtetris(c('longer names' = 30, 'but some are missing' = 23, 10))
```

### Dataframes

```{r}
counts <- data.frame(names = letters[1:4],
                     vals = c(80, 30, 20, 10))

ggtetris(counts)
```

### Colors

```{r echo=FALSE, fig.height=7}
library(patchwork)

p1 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "Vadim Gerasimov"), xlab = "Vadim Gerasimov") +
  theme(legend.position = "none")
p2 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "Microsoft"), xlab = "Microsoft") +
  theme(legend.position = "none")
p3 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "Sega"), xlab = "Sega") + 
  theme(legend.position = "none")
p4 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "The New Tetris"), xlab = "The New Tetris") +
  theme(legend.position = "none")
p5 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "The Tetris Company"), xlab = "The Tetris Company") +
  theme(legend.position = "none")
p6 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "Atari"), xlab = "Atari") +
  theme(legend.position = "none")
p7 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "The Soviet Mind Game"), xlab = "The Soviet Mind Game") +
  theme(legend.position = "none")
p8 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "Tetris DX"), xlab = "Tetris DX") +
  theme(legend.position = "none")
p9 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "Super Tetris 3"), xlab = "Super Tetris 3") +
  theme(legend.position = "none")
p10 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "Tetris Plus"), xlab = "Tetris Plus") +
  theme(legend.position = "none")
p11 <- ggtetris(rep(7, 7), colors = tetris_color(palette = "The Next Tetris"), xlab = "The Next Tetris") +
  theme(legend.position = "none")
  
p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 + p9 + p10 + p11 + plot_layout(ncol = 4)
```

## miscellaneous

```{r}
vec_named <- c('AA' = 3, 'BB' = 2, 'CC' = 1)
ggtetris_tidy(vec_named)
```

```{r}
dsamp <- diamonds[sample(nrow(diamonds), 1000), ]
ggplot(dsamp, aes(carat, price)) +
  geom_point(aes(colour = color)) + 
  scale_colour_tetris(palette = "Sega")
```


